---
title: "First Beamer"
author: "Kyle Dittmer"
date: "1/31/2018"
output: 
  beamer_presentation: 
    colortheme: beaver
    incremental: yes
    theme: Madrid
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Writing Text

Add your markdown text, etc. etc. for display on the screen, but remember, these are **slides** so we don't want too much text 

## Second slide
- First incremental bullet point
- Second incremental bullet point
- Third incremental bullet point

## Third slide
>- first simultaneous bullet point
>- second simultaneous bullet point
>- third simultaneous bullet point

## Let's see some R 
```{r}
library(ggplot2)
var1 <- runif(10)
var2 <- runif(10)
qplot(x=var1, y=var2)
```

## Colored Bullet Points
>- Collection mode
>- \color{gray} Spatial and Temporal
>- \color{red} Taxanomic bracket
>- \color{black} Sampling

## Pulling in images 

 \begin{picture}(320,250)
 \put(85,75){\includegraphics[height=6cm]
 {celtic.jpg}}
 \put(00,60){\begin{minipage}[t]{1\linewidth}
 {Choose a point on the unit circle. Connect it to 
 the origin with a line of 
 length one, and denote the angle between that line 
 and the horizontal 
 coordinate axis by $\theta$.}
 \end{minipage}}
 \end{picture}
