---
title: "Homework 6"
author: "Kyle Dittmer"
date: "2/21/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggplot2) # for graphics
library(MASS) # for maximum likelihood estimation
```

Reading in my data (crop yield per BMP)
```{r}
z <- read.table("BIO381_data.csv",header=TRUE,sep=",", stringsAsFactors=FALSE)
str(z)
summary(z)
```

Checking what the data looks like 
```{r}
p1 <- ggplot(data=z, aes(x=yld35tac, y=..density..)) + geom_histogram(color="grey60",fill="cornsilk",size=0.2)
print(p1)
```

Adding empirical density curve
```{r}
p1 <-  p1 +  geom_density(linetype="dotted",size=0.75)
print(p1)
```

Get maximum likelihood parameters for normal
```{r}
normPars <- fitdistr(z$yld35tac,"normal")
print(normPars) # gives mean and standard deviation
str(normPars)
normPars$estimate["mean"] # easier way to get the mean value
```


Plot normal probability density
```{r}
meanML <- normPars$estimate["mean"]
sdML <- normPars$estimate["sd"]

xval <- seq(0,max(z$yld35tac),len=length(z$yld35tac))

 stat <- stat_function(aes(x = xval, y = ..y..), fun = dnorm, colour="red", n = length(z$yld35tac), args = list(mean = meanML, sd = sdML))
 p1 + stat
```

Plotting with exponential function
```{r}
expoPars <- fitdistr(z$yld35tac,"exponential")
rateML <- expoPars$estimate["rate"]

stat2 <- stat_function(aes(x = xval, y = ..y..), fun = dexp, colour="blue", n = length(z$yld35tac), args = list(rate=rateML))
 p1 + stat + stat2
```

Plotting uniform probability denisty 
```{r}
stat3 <- stat_function(aes(x = yld35tac, y = ..y..), fun = dunif, colour="darkgreen", n = length(z$yld35tac), args = list(min=min(z$yld35tac), max=max(z$yld35tac)))
 p1 + stat + stat2 + stat3
```

Plotting gamma probability density
```{r}
gammaPars <- fitdistr(z$yld35tac,"gamma")
shapeML <- gammaPars$estimate["shape"]
rateML <- gammaPars$estimate["rate"]

stat4 <- stat_function(aes(x = xval, y = ..y..), fun = dgamma, colour="goldenrod", n = length(z$yld35tac), args = list(shape=shapeML, rate=rateML))
 p1 + stat + stat2 + stat3 + stat4
```

Plotting beta probability density
```{r}
pSpecial <- ggplot(data=z, aes(x=yld35tac/(max(yld35tac + 0.1)), y=..density..)) +
  geom_histogram(color="grey60",fill="cornsilk",size=0.2) + 
  xlim(c(0,1)) +
  geom_density(size=0.75,linetype="dotted")

betaPars <- fitdistr(x=z$yld35tac/max(z$yld35tac + 0.1),start=list(shape1=1,shape2=2),"beta")
shape1ML <- betaPars$estimate["shape1"]
shape2ML <- betaPars$estimate["shape2"]

statSpecial <- stat_function(aes(x = yld35tac, y = ..y..), fun = dbeta, colour="orchid", n = length(z$yld35tac), args = list(shape1=shape1ML,shape2=shape2ML))
pSpecial + statSpecial
```

Finding the best fit distibution
```{r}
normPars$loglik # -93.52484
gammaPars$loglik # -93.76825
# Normal wins!
```


Simulating my data based on a normal distribution
```{r}
print(stat)
length(z$yld35tac)
simNorm <- as.data.frame(rnorm(n=41,mean= 21.4192438914634, sd=2.3682588855803))

names(simNorm) <- "yld35tac"

p2 <- ggplot(data = simNorm, aes(x=yld35tac,y=..density..)) + geom_histogram(color="grey60",fill="cornsilk",size=0.2)

p2 + stat
```

